### 2022-08-09 viz/figures.Rmd
Some small changes from our journal article revision

```{r fig2, fig.width = 5.5, fig.height = 3}

@@

d_prime_age_pointrange <- ggplot(kids$d$ages %>% bind_rows(), 
                                 aes(x = age, y = d_prime,
                                 colour = factor(type, levels = c("dance",  "lullaby", "healing"))
                     )) +
  geom_smooth(method = "lm",
              aes(group = type), alpha = .3, key_glyph = "pointrange") +
  geom_pointrange(aes(ymin = conf.low, ymax = conf.high), fatten = 5, size = .3,
                  position = position_dodge(width = .3), alpha = .8, pch = 16,
                  key_glyph = "pointrange") +
  geom_hline(yintercept = 0, linetype = "dashed", color = "black") +
  scale_x_continuous(breaks = seq(from = 1, to = 17, by = 1)) +
  scale_colour_manual(values = c("#619CFF", "#00BA38","#F8766D"),
                      name = "",
                      labels = c("Dance", "Lullaby", "Healing")) +
  labs(x = "Age (Years)", y = "") +
  scale_y_continuous(breaks = seq(0,2,1/5)) +
  coord_cartesian(ylim = c(0,1.8), clip = "off") +
  theme_bw() +
  theme(panel.grid.minor.x = element_blank(),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank())

fig2 <- d_prime_pointrange + d_prime_age_pointrange +
  plot_annotation(tag_levels = "a") +
  plot_layout(widths = c(1,4))

>>>>

```{r fig2, fig.width = 6.2, fig.height = 3}

@@

d_prime_age_pointrange <- ggplot(kids$d$ages %>% bind_rows(), 
       aes(x = age, y = d_prime,
           colour = factor(type, levels = c("dance",  "lullaby", "healing"))
       )) +
  geom_smooth(method = "lm",
              aes(group = type), alpha = .3, key_glyph = "pointrange") +
  geom_pointrange(aes(ymin = conf.low, ymax = conf.high), fatten = 5, size = .3,
                  position = position_dodge(width = .3), alpha = .8, pch = 16,
                  key_glyph = "pointrange") +
  # ADDING ADULT DATA
  geom_point(data = bind_rows(adults$d$group) %>% 
               filter(type != "love") %>%
               mutate(age = 19),
             size = 2.5, alpha = .8, pch = 17,show.legend = FALSE) +
  # ADDING SEPARATION LINE
  annotate("segment", x = 17.5, xend = 17.5, y = 0.1, yend = 1.8, colour = "black", size = 0.2) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "black") +
  scale_x_continuous(breaks = c(seq(from = 1, to = 16, by = 1), 16, 16, 19, 19), 
                     labels = c(seq(from = 1, to = 16, by = 1), " ", " ", "Adults", " ")) +
  scale_colour_manual(values = c("#619CFF", "#00BA38","#F8766D"),
                      name = "",
                      labels = c("Dance", "Lullaby", "Healing")) +
  labs(x = "Age (Years)", y = "") +
  scale_y_continuous(breaks = seq(0,2,1/5)) +
  coord_cartesian(ylim = c(0,1.8), xlim = c(4,20)) +
  theme_bw() +
  theme(panel.grid.minor.x = element_blank(),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank())

fig2 <- d_prime_pointrange + d_prime_age_pointrange +
  plot_annotation(tag_levels = "a") +
  plot_layout(widths = c(1,5))

### 2022-08-09 writing/manuscript.Rmd
Some small changes from our journal article revision

---
bibliography: themusiclab.bib
csl: apa.csl
header-includes:
- \usepackage{ragged2e}
- \usepackage{caption}
- \captionsetup[figure]{labelformat=empty}
- \usepackage{tabu}
- \usepackage{afterpage}
- \usepackage{mdframed}
- \usepackage{xcolor}
- \usepackage{soul}
- \usepackage{float}
- \definecolor{bleu}{HTML}{2200cc}
notes-after-punctuation: no
output:
  pdf_document: 
    fig_caption: yes
    latex_engine: xelatex
  word_document: default
urlcolor: bleu
link-citations: yes
linkcolor: bleu
always_allow_html: yes
---

@@

@@

\footnotesize
$^{1}$Haskins Laboratories, New Haven, CT 06511, USA.\
$^{2}$Department of Psychology, Harvard University, Cambridge, MA 02138, USA.\
$^{3}$School of Psychology, Victoria University of Wellington, Wellington 6012, New Zealand.\
$^{4}$Department of Psychology, University of Michigan, Ann Arbor, MI 48109, USA.\
$^{5}$Data Science Initiative, Harvard University, Cambridge, MA 02138, USA.

@@

\*Corresponding author. Emails: [courtneyhilton\@g.harvard.edu](mailto:courtneyhilton@g.harvard.edu){.email}, [liam.crowleydethierry\@vuw.ac.nz](mailto:liam.crowleydethierry@vuw.ac.nz){.email}, [sam\@wjh.harvard.edu](mailto:sam@wjh.harvard.edu){.email}

@@

Whereas some musical contexts are idiosyncratic, as in the encoding of complex geographical knowledge in song by some groups of Indigenous Australians [@Norris2014], other contexts are recurrent across societies and tend to co-occur with the same acoustic features. For example, lullabies tend to have slow tempos; smooth, minimally accented contours; and a narrow dynamic and pitch range, as has been long-established in western societies [@Bergeson1999; @Trehub1998a; @Trehub1993], and recently in more globally representative samples of societies [@Hilton2021a; @Mehr2019]. The findings that music appears universally in conjunction with particular behavioral contexts (e.g., infant care), and that examples of music in a given context share particular acoustic features (e.g., minimal accents), imply a link between form and function in music production.

@@

```{r fig1}
#| fig.cap = "\\textbf{Figure 1.} Schematic of the test phase of the experiment. Children listened to the songs and indicated their responses in the context of an online game. \\textbf{a}, Parents guided their children's participation with the assistance of a progress bar, which indicated which portions of the experiment were intended to be for parents alone, parents and children together, or children alone. The progress bar was visible throughout the experiment. \\textbf{b}, The game was narrated by \\textit{Susie the Star}, an animated character whose instructions were spoken aloud and printed in speech bubbles on the screen. \\textbf{c}, During testing children listened to a series of songs. \\textbf{d}, After each song, \\textit{Susie} asked them to guess its behavioral context and indicate their response by clicking or tapping an image (with accompanying text)."
knitr::include_graphics(here("viz", "figures", "fig1-1-mod.pdf"))
```

@@

Last, parents answered debriefing questions. The questions confirmed whether the child had worn headphones during the experiment (if, at the beginning of the study, the parent had stated the child would wear headphones), if the parent had assisted the child during the training portion of the experiment, and if the parent had assisted the child during the test questions (those who had were excluded from analyses; see Participants, above).

@@

In designing the experiment, we first piloted the experiment in-person with four children (ages 6, 7, 9, and 10), to explore whether the procedure was well-explained and intuitive for chilren, and to observe potential parental interference. The children easily understood the task and did not elicit help from their parents; at times they *rejected* parental assistance (e.g., as if to say "I can do this on my own, mum").

@@

Most psychological studies of children are conducted in-person (e.g., in a laboratory or school) or in a moderated online setting (e.g., via videoconference). Our approach instead relies on an unmoderated, *citizen-science* approach. While this approach has the advantage of larger-scale, and often more diverse recruitment than in-person or moderated online studies [@Hilton2022; @LiSubmitted], it has two potential risks.

@@

As no compensation was given, it is not clear what incentive there would be for either possibility, and there is growing evidence that uncompensated online and compensated lab-based data collection produce similar results across a number of domains [@Huber2020; @Hartshorne2019; @Germine2012]. Nevertheless, we analyzed several forms of metadata to explore the risk of participant misrepresentation.

@@

Second, at the completion of the online experiment, we explicitly asked parents whether they complied with the request to not interfere with the child's performance. Post-hoc prompts on task compliance have been shown to be effective in other uncompensated online experiments [@Reinecke2015]; parents have little incentive to lie in response to such a question. The vast majority of parents stated that they did not assist their children in the experiment and we excluded those who did (see Participants, above).

@@

```{r fig2}
#| fig.cap = "\\textbf{Figure 2 | Accurate classification of all three song types and cohort-wide, with no effect of age.} (\\textbf{a}) Mean *d*-prime scores across all children show above-chance classification of each song type, independent of their response bias. (\\textbf{b}) Above-chance sensitivity replicates for each age group, except for some of the healing song estimates whose 95% confidence-intervals crossed zero. Performance did not improve with age, either averaging across all song-types, or within dance, lullaby, or healing songs individually (ps > 0.05). In both panels, the circles indicate *d*-prime scores and the error bars indicate the 95% confidence intervals. In panel \\textbf{b}, the three thick lines depict a linear regression for each song type and the shaded regions represent the 95% confidence intervals from each regression."
knitr::include_graphics(here("viz", "figures", "fig2-1.pdf"))
```

@@

Previous work demonstrated that a core set of musical features reliably distinguished dance songs, lullabies, and healing songs from one another across 30 world regions [@Mehr2019]. In an exploratory test of our fifth preregistered hypothesis, we tested the degree to which chilren's inferences reflected these universal musical biases.

@@

We found that children make accurate inferences concerning the behavioral contexts of unfamiliar foreign lullabies, dance songs, and healing songs. The songs were unfamiliar to the children and drawn from a representative sample of vocal music from `r length(unique(songs$culture))` human societies, but their guessing patterns were well above chance and strikingly similar to those of adults. Older children (teenagers) performed no better than the youngest chilren in our sample (age 4), who already performed at adult-like levels. Musical exposure in the home, from either recorded music or parental singing, was also unrelated to children's performance. These results suggest that the ability to infer musical function from acoustical forms, at least in the contexts studied here, develops early and requires minimal direct experience.

@@

What explains these robust associations between musical features and functional inferences? We speculate that they tie into the prototypical emotional and physiological content of songs' behavioral contexts. Across cultures, dance songs typically aim to increase arousal (e.g., energizing groups of people to dance) whereas lullabies aim to decrease it [e.g., soothing an infant: @Hilton2021a; @Mehr2019]. This is mirrored in the arousal-mediating effects of both rhythmic accentuation [@Weninger2013; @Ilie2006; @Schubert2004] and tempo [@Yamamoto2007; @Husain2002; @Balch1996; @Holbrook1990]. As in other universal acoustic form-function mappings [@Perlman2021; @Patten2018; @Fitch2002; @Fitch1997], this relationship may be grounded in the physics of sound production: the production of sounds with high tempo and accentuation, for example, requires more energy than does the production of slower, less accentuated sounds. These features are thus associated with higher arousal. Indeed, from a young age, infant arousal is reliably modulated by these features [@Bainbridge2021; @Cirelli2019].

@@

Together, our findings suggest that some form-function inferences about music may be maturational rather than experiential in origin: requiring minimal direct experience to develop. Many other facets of music perception develop precocially in this way, including beat processing [@Zentner2010; @Winkler2009; @Phillips-Silver2005]; sensitivity to basic tonal structure [@Perani2010; @Lynch1992]; prenatally present attentional orientations to music [@Granier-Deferre2011]; biases for socially-relevant musical information [@Mehr2016; @Mehr2017]; and indeed, distinct physiological responses to lullabies, relative to non-lullabies [@Bainbridge2021]. Some of these abilities continue to develop with experience; for example, in the first year of life, the perception of metrical [@Hannon2005] and tonal [@Lynch1990] structures becomes tuned to regularities of the infants' native musical culture, and later stages of this can even continue past 12 years of age in ways that depend upon rich experiential input [@Brandt2012]. By contrast, the present findings show an adult-like competence as late as 4 years of age (and potentially earlier; see SI Text 1), irrespective of variation in musical exposure.

This is not to say that experience does *not* shape listeners' understanding of music. Experience shapes many facets of musicality, from musical preferences [@Schellenberg2008b; @Peretz1998], to the enculturation of extramusical associations [@Margulis2022]. Experience can even exert subtle influences on our perception of basic structures of rhythm [@Drake2003] and pitch [@Jacoby2019]; the influences are not be limited to *musical* experience, as shown by the effect of linguistic experiences on music processing [@Liu2021]. And while we studied a relatively diverse sample of children and a highly diverse set of recordings (see SI Tables 1-3), we did not systematically sample diverse experiences: the study instructions were in English and the children were recruited via an English-language website. These limitations suggest a need for further studies conducted in multiple languages and recruiting from a wide variety of geographic regions, so as to better characterize the potential effects of early musical experience on listeners' understanding of music.

@@

This research builds on previous studies from our group [@Mehr2019; @Mehr2018a; @Hilton2021a], demonstrating (a) cross-cultural regularities in the associations between acoustical forms of music and particular behavioral contexts in which music appears; and (b) the sensitivity of adults to these associations. Here, we explored how musical experience in childhood shapes that sensitivity, using the same stimuli as previous work. We also compared children's intuitions about music to adults' directly, and analyzed how these intuitions correlate with specific musical features (providing clues about the mechanisms underlying the main effects). The results complement those of another recent study [@Bainbridge2021], where infants showed differential physiological responses to unfamiliar foreign lullabies, relative to non-lullabies; those early-appearing, implicit responses to different forms of music, may help to explain children's high performance in classifying behavioral contexts for music. Together, these studies inform theories of the basic design features of a human psychology of music, including debates surrounding the biological foundations of music [@Mehr2020] and its relation to more general aspects of cognition [@Hilton2020].

@@

- S.A.M. and A.M. conceived of the research and provided funding and other resources. 
- L.C-T., A.M., and S.A.M. designed the experiment.
- L.C-T. wrote code to implement the experiment, with contributions from S.A.M.
- L.C-T., A.M., and S.A.M. piloted the experiment.
- L.C-T., C.B.H., and S.A.M. collected the data. 
- C.B.H. led analyses and designed the figures, with contributions from L.C-T., R.Y., A.M., and S.A.M.
- C.B.H. and S.A.M. wrote the original manuscript, with contributions from L.C-T., R.Y., and A.M.
- C.B.H. wrote the revision, with contributions from L.C-T and S.A.M., and all authors approved it.

@@

songs %>% 
  select(song, type, culture, country) %>% 
  left_join(., NHS_languages %>% select(track, language), by = c("song" = "track")) %>% 
  mutate(song = row_number()) %>% 
  rename_with(~str_to_title(.), everything()) %>% 
  rename(`Modern-Day Country` = Country) %>% 
  kbl(., 
      col.names = c("Song ID", "Type", "Society", "Country (present-day)", "Language"),
      longtable = TRUE, booktabs = TRUE, linesep = "", align = "l") %>% 
  kable_styling(latex_options = c("repeat_header"),
                font_size = 7) %>% 
  footnote(general = "Summary information about the songs chilren heard.",
           general_title = "SI Table 3",
           title_format = "bold",
           footnote_as_chunk = TRUE,
           threeparttable = TRUE) %>% 
  column_spec(1, width = "0.3in") %>% 
  column_spec(2, width = "0.6in") %>% 
  column_spec(3, width = "1.4in") %>% 
  column_spec(4, width = "1.8in") %>%
  column_spec(5, width = "1.4in")

@@

# dance
regression_table2(mods$equiv2$full$dance, 
                  c(
                    "Intercept",
                    "Accentuation",
                    "Tempo",
                    "Metrical clarity",
                    "Duple rhythm",
                    "Note duration"
                  ),
                  "Musical features influencing children's \`\`dance\" guesses, compared to the features that objectively distinguish song types from one another. The LASSO-selected correlates for children are listed on the left side of the table; those that reliably correlate with song types across world regions are on the right side and are tested relative to the children (i.e., from the interaction terms in the model). Contrasting SI Tables 5-7, quite a few features differ significantly, indicating that in many cases, chilren's intuitions (erroneously) deviate from the objective differences between song types.",
                  8)
# lullaby
regression_table2(mods$equiv2$full$lullaby, 
                  c(
                    "Intercept",
                    "Accentuation",
                    "Melodic simplicity",
                    "Tempo",
                    "Note duration",
                    "Maj(-)/min(+) tonality",
                    "Melodic ornamentation",
                    "Intervallic distinctiveness",
                    "Note density",
                    "Metrical clarity",
                    "Vibrato",
                    "Duple meter"
                  ),
                  "Musical features influencing children's \`\`lullaby\" guesses, compared to the features that objectively distinguish song types from one another. The LASSO-selected correlates for children are listed on the left side of the table; those that reliably correlate with song types across world regions are on the right side and are tested relative to the children (i.e., from the interaction terms in the model). Contrasting SI Tables 5-7, quite a few features differ significantly, indicating that in many cases, chilren's intuitions (erroneously) deviate from the objective differences between song types.",
                  9)

# healing
regression_table2(mods$equiv2$full$healing, 
                  c(
                    "Intercept",
                    "Metrical clarity",
                    "Tempo",
                    "Maj(-)/min(+) tonality",
                    "Sycopation",
                    "Vibrato",
                    "Melodic simplicity"
                  ),
                  "Musical features influencing children's \`\`healing\" guesses, compared to the features that objectively distinguish song types from one another. The LASSO-selected correlates for children are listed on the left side of the table; those that reliably correlate with song types across world regions are on the right side and are tested relative to the children (i.e., from the interaction terms in the model). Contrasting SI Tables 5-7, quite a few features differ significantly, indicating that in many cases, chilren's intuitions (erroneously) deviate from the objective differences between song types.",
                  10)

>>>>

---
bibliography: themusiclab.bib
csl: apa.csl
header-includes:
- \usepackage{ragged2e}
- \usepackage{caption}
- \captionsetup[figure]{labelformat=empty}
- \usepackage{tabu}
- \usepackage{afterpage}
- \usepackage{mdframed}
- \usepackage{xcolor}
- \usepackage{soul}
- \usepackage{float}
- \definecolor{bleu}{HTML}{2200cc}
notes-after-punctuation: no
output:
  pdf_document:
    fig_caption: yes
    latex_engine: xelatex
  word_document: default
  html_document:
    df_print: paged
urlcolor: bleu
link-citations: yes
linkcolor: bleu
always_allow_html: yes
---

@@

\normalsize
\textbf{NOTE:} This manuscript has now been accepted at The Journal of Experimental Psychology: General, and should be cited as: Hilton, C. B., Crowley-de Thierry, L., Yan, R., Martin, A., & Mehr, S. A. (2022). Children infer the behavioral contexts of unfamiliar foreign songs. *Journal of Experiment Psychology: General*.

@@

\footnotesize
$^{1}$Haskins Laboratories, Yale University, New Haven, CT 06511, USA.\
$^{2}$Department of Psychology, Harvard University, Cambridge, MA 02138, USA.\
$^{3}$School of Psychology, Victoria University of Wellington, Wellington 6012, New Zealand.\
$^{4}$Department of Psychology, University of Michigan, Ann Arbor, MI 48109, USA.\
$^{5}$Data Science Initiative, Harvard University, Cambridge, MA 02138, USA.

@@

\*Corresponding author. Emails: [courtney.hilton\@yale.edu](mailto:courtney.hilton@yale.edu){.email}, [liam.crowleydethierry\@vuw.ac.nz](mailto:liam.crowleydethierry@vuw.ac.nz){.email}, [sam\@wjh.harvard.edu](mailto:sam@wjh.harvard.edu){.email}

@@

Whereas some musical contexts are idiosyncratic, as in the encoding of complex geographical knowledge in song by some groups of Indigenous Australians [@Norris2014], other contexts are recurrent across societies and tend to co-occur with the same acoustic features. For example, lullabies tend to have slow tempos; smooth, minimally accented contours; and a narrow dynamic and pitch range, as has been long-established in western societies [@Bergeson1999; @Trehub1998a; @Trehub1993], and recently in more globally representative samples of societies [@Hilton2022a; @Mehr2019]. The findings that music appears universally in conjunction with particular behavioral contexts (e.g., infant care), and that examples of music in a given context share particular acoustic features (e.g., minimal accents), imply a link between form and function in music production.

@@

```{r fig1}
#| fig.cap = "\\textbf{Figure 1.} Schematic of the test phase of the experiment. Children listened to the songs and indicated their responses in the context of an online game. \\textbf{a}, Parents guided their children's participation with the assistance of a progress bar, which indicated which portions of the experiment were intended to be for parents alone, parents and children together, or children alone. The progress bar was visible throughout the experiment. \\textbf{b}, The game was narrated by \\textit{Susie the Star}, an animated character whose instructions were spoken aloud and printed in speech bubbles on the screen. \\textbf{c}, During testing children listened to a series of songs. \\textbf{d}, After each song, \\textit{Susie} asked them to guess its behavioral context and indicate their response by clicking or tapping an image (with accompanying text)."
knitr::include_graphics(here("viz", "figures", "fig1-1.pdf"))
```

@@

Last, parents answered debriefing questions. The questions confirmed whether the child had worn headphones during the experiment (if, at the beginning of the study, the parent had stated the child would wear headphones; we decided to not exclude based on headphone usage as it made no discernible difference), if the parent had assisted the child during the training portion of the experiment, and if the parent had assisted the child during the test questions (those who had were excluded from analyses; see Participants, above).

@@

In designing the experiment, we first piloted the experiment in-person with four children (ages 6, 7, 9, and 10), to explore whether the procedure was well-explained and intuitive for children, and to observe potential parental interference. The children easily understood the task and did not elicit help from their parents; at times they *rejected* parental assistance (e.g., as if to say "I can do this on my own, mum").

@@

Most psychological studies of children are conducted in-person (e.g., in a laboratory or school) or in a moderated online setting (e.g., via videoconference). Our approach instead relies on an unmoderated, *citizen-science* approach. While this approach has the advantage of larger-scale, and often more diverse recruitment than in-person or moderated online studies [@Hilton2022; @Li2022], it has two potential risks.

@@

As no compensation was given, it is not clear what incentive there would be for either possibility, and there is growing evidence that compared to traditional compensated lab-based data collection, comparable results can be reliably obtained across a number of domains using online data collection with either compensated [@Coppock2019; @Ratcliff2021] or uncompensated [@Huber2020; @Hartshorne2019; @Germine2012] recruitment. Nevertheless, we analyzed several forms of metadata to explore the risk of participant misrepresentation.

@@

Second, at the completion of the online experiment, we explicitly asked parents whether they complied with the request to not interfere with the child's performance. Post-hoc prompts on task compliance have been shown to be effective in other uncompensated online experiments [@Reinecke2015]; parents have little incentive to lie in response to such a question. The vast majority of parents stated that they did not assist their children in the experiment and we excluded those who did (see Participants, above). However, we cannot rule out the possibility that parents implicitly affected their child's performance without intending to.

@@

```{r fig2}
#| fig.cap = "\\textbf{Figure 2 | Accurate classification of all three song types and cohort-wide, with no effect of age.} (\\textbf{a}) Mean *d*-prime scores across all children show above-chance classification of each song type, independent of their response bias. (\\textbf{b}) Above-chance sensitivity replicates for each age group, except for some of the healing song estimates whose 95% confidence-intervals crossed zero. Performance did not improve with age, either averaging across all song-types, or within dance, lullaby, or healing songs individually (ps > 0.05). As a reference, the rightmost triangular points depict performance in a similar experiment with 98,150 adults between 18 and 99 years of age (mean 31 years). Small differences in task demands make strict comparison to the children problematic, but qualitatively, they show comparable performance. In both panels, the circles indicate *d*-prime scores and the error bars indicate the 95% confidence intervals. In panel \\textbf{b}, the three thick lines depict a linear regression for each song type and the shaded regions represent the 95% confidence intervals from each regression."
knitr::include_graphics(here("viz", "figures", "fig2-1.pdf"))
```

@@

Previous work demonstrated that a core set of musical features reliably distinguished dance songs, lullabies, and healing songs from one another across 30 world regions [@Mehr2019]. In an exploratory test of our fifth preregistered hypothesis, we tested the degree to which children's inferences reflected these universal musical biases.

@@

We found that children make accurate inferences concerning the behavioral contexts of unfamiliar foreign lullabies, dance songs, and healing songs. The songs were unfamiliar to the children and drawn from a representative sample of vocal music from `r length(unique(songs$culture))` human societies, but their guessing patterns were well above chance and strikingly similar to those of adults. Older children (teenagers) performed no better than the youngest children in our sample (age 4), who already performed at adult-like levels. Musical exposure in the home, from either recorded music or parental singing, was also unrelated to children's performance. These results suggest that the ability to infer musical function from acoustical forms, at least in the contexts studied here, develops early and requires minimal direct experience.

@@

What explains these robust associations between musical features and functional inferences? We speculate that they tie into the prototypical emotional and physiological content of songs' behavioral contexts. Across cultures, dance songs typically aim to increase arousal (e.g., energizing groups of people to dance) whereas lullabies aim to decrease it [e.g., soothing an infant: @Hilton2022a; @Mehr2019]. This is mirrored in the arousal-mediating effects of both rhythmic accentuation [@Weninger2013; @Ilie2006; @Schubert2004] and tempo [@Yamamoto2007; @Husain2002; @Balch1996; @Holbrook1990]. As in other universal acoustic form-function mappings [@Perlman2021; @Patten2018; @Fitch2002; @Fitch1997], this relationship may be grounded in the physics of sound production: the production of sounds with high tempo and accentuation, for example, requires more energy than does the production of slower, less accentuated sounds. These features are thus associated with higher arousal. Indeed, from a young age, infant arousal is reliably modulated by these features [@Bainbridge2021; @Cirelli2019].

@@

Together, our findings suggest that some form-function inferences about music may be more maturational rather than experiential in origin: requiring minimal direct experience to develop an initial capacity. Many other facets of music perception develop precocially in this way, including beat processing [@Zentner2010; @Winkler2009; @Phillips-Silver2005]; sensitivity to basic tonal structure [@Perani2010; @Lynch1992]; prenatally present attentional orientations to music [@Granier-Deferre2011]; biases for socially-relevant musical information [@Mehr2016; @Mehr2017]; and indeed, distinct physiological responses to lullabies, relative to non-lullabies [@Bainbridge2021]. Some of these abilities continue to develop with experience; for example, in the first year of life, the perception of metrical [@Hannon2005] and tonal [@Lynch1990] structures becomes tuned to regularities of the infants' native musical culture, and later stages of this can even continue past 12 years of age in ways that depend upon rich experiential input [@Brandt2012]. By contrast, the present findings show an adult-like competence as late as 4 years of age (and potentially earlier; see SI Text 1), irrespective of variation in musical exposure.

This is not to say that experience does *not* shape listeners' understanding of music. Experience shapes many facets of musicality, from musical preferences [@Schellenberg2008b; @Peretz1998], to the enculturation of extramusical associations [@Margulis2022]. Experience can even exert subtle influences on our perception of basic structures of rhythm [@Drake2003] and pitch [@Jacoby2019]; the influences need not be limited to *musical* experience, as shown by the effect of linguistic experiences on music processing [@Liu2021]. And while we studied a relatively diverse sample of children and a highly diverse set of recordings (see SI Tables 1-3), we did not systematically sample diverse experiences: the study instructions were in English and the children were recruited via an English-language website. These limitations suggest a need for further studies conducted in multiple languages and recruiting from a wide variety of geographic regions, so as to better characterize the potential effects of early musical experience on listeners' understanding of music.

@@

This research builds on previous studies from our group [@Mehr2019; @Mehr2018a; @Hilton2022a], demonstrating (a) cross-cultural regularities in the associations between acoustical forms of music and particular behavioral contexts in which music appears; and (b) the sensitivity of adults to these associations. Here, we explored how musical experience in childhood shapes that sensitivity, using the same stimuli as previous work. We also compared children's intuitions about music to adults' directly, and analyzed how these intuitions correlate with specific musical features (providing clues about the mechanisms underlying the main effects). The results complement those of another recent study [@Bainbridge2021], where infants showed differential physiological responses to unfamiliar foreign lullabies, relative to non-lullabies; those early-appearing, implicit responses to different forms of music, may help to explain children's high performance in classifying behavioral contexts for music. Together, these studies inform theories of the basic design features of a human psychology of music, including debates surrounding the biological foundations of music [@Mehr2020] and its relation to more general aspects of cognition [@Hilton2020].

@@

- S.A.M. and A.M. conceived of the research and provided funding and other resources. 
- L.C-T., A.M., and S.A.M. designed the experiment.
- L.C-T. wrote code to implement the experiment, with contributions from S.A.M.
- L.C-T., A.M., and S.A.M. piloted the experiment.
- L.C-T., C.B.H., and S.A.M. collected the data. 
- C.B.H. led analyses and designed the figures, with contributions from L.C-T., R.Y., A.M., and S.A.M.
- C.B.H. and S.A.M. wrote the original manuscript, with contributions from L.C-T., R.Y., and A.M.
- C.B.H. wrote the revision, with contributions from L.C-T and S.A.M., and all authors approved it.
- C.B.H. wrote the second revision, with contributions from L.C-T and S.A.M., and all authors approved it.

@@

songs %>% 
  select(song, type, culture, country) %>% 
  left_join(., NHS_languages %>% select(track, language), by = c("song" = "track")) %>% 
  mutate(song = row_number()) %>% 
  rename_with(~str_to_title(.), everything()) %>% 
  rename(`Modern-Day Country` = Country) %>% 
  kbl(., 
      col.names = c("Song ID", "Type", "Society", "Country (present-day)", "Language"),
      longtable = TRUE, booktabs = TRUE, linesep = "", align = "l") %>% 
  kable_styling(latex_options = c("repeat_header"),
                font_size = 7) %>% 
  footnote(general = "Summary information about the songs children heard.",
           general_title = "SI Table 3",
           title_format = "bold",
           footnote_as_chunk = TRUE,
           threeparttable = TRUE) %>% 
  column_spec(1, width = "0.3in") %>% 
  column_spec(2, width = "0.6in") %>% 
  column_spec(3, width = "1.4in") %>% 
  column_spec(4, width = "1.8in") %>%
  column_spec(5, width = "1.4in")

@@

# dance
regression_table2(mods$equiv2$full$dance, 
                  c(
                    "Intercept",
                    "Accentuation",
                    "Tempo",
                    "Metrical clarity",
                    "Duple rhythm",
                    "Note duration"
                  ),
                  "Musical features influencing children's \`\`dance\" guesses, compared to the features that objectively distinguish song types from one another. The LASSO-selected correlates for children are listed on the left side of the table; those that reliably correlate with song types across world regions are on the right side and are tested relative to the children (i.e., from the interaction terms in the model). Contrasting SI Tables 5-7, quite a few features differ significantly, indicating that in many cases, children's intuitions (erroneously) deviate from the objective differences between song types.",
                  8)
# lullaby
regression_table2(mods$equiv2$full$lullaby, 
                  c(
                    "Intercept",
                    "Accentuation",
                    "Melodic simplicity",
                    "Tempo",
                    "Note duration",
                    "Maj(-)/min(+) tonality",
                    "Melodic ornamentation",
                    "Intervallic distinctiveness",
                    "Note density",
                    "Metrical clarity",
                    "Vibrato",
                    "Duple meter"
                  ),
                  "Musical features influencing children's \`\`lullaby\" guesses, compared to the features that objectively distinguish song types from one another. The LASSO-selected correlates for children are listed on the left side of the table; those that reliably correlate with song types across world regions are on the right side and are tested relative to the children (i.e., from the interaction terms in the model). Contrasting SI Tables 5-7, quite a few features differ significantly, indicating that in many cases, children's intuitions (erroneously) deviate from the objective differences between song types.",
                  9)

# healing
regression_table2(mods$equiv2$full$healing, 
                  c(
                    "Intercept",
                    "Metrical clarity",
                    "Tempo",
                    "Maj(-)/min(+) tonality",
                    "Sycopation",
                    "Vibrato",
                    "Melodic simplicity"
                  ),
                  "Musical features influencing children's \`\`healing\" guesses, compared to the features that objectively distinguish song types from one another. The LASSO-selected correlates for children are listed on the left side of the table; those that reliably correlate with song types across world regions are on the right side and are tested relative to the children (i.e., from the interaction terms in the model). Contrasting SI Tables 5-7, quite a few features differ significantly, indicating that in many cases, children's intuitions (erroneously) deviate from the objective differences between song types.",
                  10)
